TBA

### 2019-10-07 paper.tex
Added Fitts IP figure, explanation

Analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
A post-hoc analysis using the Wilcoxon signed rank test with a Holm-Bonferoni correction applied to the commonly used 0.05 statistical significance threshold was used to investigate the setting relationships more closely. 
This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
With these results, we can reasonably conclude that the \textit{hi} setting  
The distributions in \cref{fig:target-boxplot-error} show that the \textit{hi} setting produces the smallest median angular error in the elevation dimension out of the 3 settings and the post-hoc tests performed allow us to make the conclusion that the \textit{hi} setting is indeed the best setting to produce the lowest error.

@@

For Group \textit{G1}, a Fitts relationship can be observed where the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.9, p_{lo} = 0.03; r_{med} = 0.92, p_{med}=0.009; r_{hi} = 0.86, p_{hi} = 0.02$).
This result allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-ip}, for each setting in \cref{fig:fitts-ips}.

@@

>>>>

Analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
A post-hoc analysis using the Wilcoxon signed rank test with a Holm-Bonferoni correction applied to the commonly used 0.05 statistical significance threshold was used to investigate the setting relationships more closely. 
This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
It can also be noted that there is a significant negative error bias observed in all of the settings in both groups which is possible caused by a cognitive constraint introduced by the floor where the participants believed that the targets could not appear below the ground.
Since this bias seems constant in nature, it can be addressed by adjusting the frequency parameters of the interface and shifting it by a constant offset.

With these results, we can reasonably conclude that the \textit{hi} setting  
The distributions in \cref{fig:target-boxplot-error} show that the \textit{hi} setting produces the smallest median angular error in the elevation dimension out of the 3 settings and the post-hoc tests performed allow us to make the conclusion that the \textit{hi} setting is indeed the best setting to produce the lowest error.

@@

For Group \textit{G1}, a Fitts relationship can be observed where the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.9, p_{lo} = 0.03; r_{med} = 0.92, p_{med}=0.009; r_{hi} = 0.86, p_{hi} = 0.02$).
Regarding Group \textit{G2}¸ we observe larger spreads for each binned dataset, indicating less consistency int eh time to target results for participants with severe sight impairments.
However, the results for the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88, p_{med} = 0.019; r_{hi} = 0.89, p_{med} = 0.03$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.23, p_{lo} = 0.65$).

These results allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-ip}, for each setting in \cref{fig:fitts-ips}.

@@

For the results from Group\textit{G1}, there is a progressive improvement in performance between the \textit{lo}, \textit{med} and \textit{hi} settings respectively, with the \textit{hi} producing the highest level of performance between the 3 settings, i.e.\ the participants found the targets with the smallest error in the least about of time with the \textit{hi} setting.
This is supported by the results from the Friedman test ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show all 3 datasets are significantly different from one another ($p_{lo} = p_{med} = p_{hi} < 0.001$).
The results for Group \textit{G2} shows far lower indices of performance for each setting, which is expected given the increased indices of difficulty observed in \cref{fig:fitts-results}.
Indeed, the distributions are shown to be similar according to the Friedman test ($p = 0.1$) and we cannot conclude which setting produces the best performance. 
\todo{explain why bad}
